### 2024-02-13 output/paper.qmd
paper

---
title: "Digital Addiction"
subtitle: "My subtitle if needed"
author: 
  - Kenneth Chan, Stephanie Xuan Zhao, Siyu Li
thanks: "Code and data are available at: <https://github.com/YO7O/digital_addiction.git>"
date: today
date-format: long
abstract: "."
format: pdf
number-sections: true
#bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

```

# Introduction
In 2023, there will be more than 4.95 billion users of different social media across the world. It has rapidly increased since 2015, as it only had 2.05 billion social media users at that time. (backlinko) According to Datareportal, in quarter 3 of 2021, it shows  46% of Americans spend 4 to 5 hours every day on their phones and 1 in 5 people have more than 4.5 hours per day of usage of their phone. With the development of technology, smartphones have started to offer more services and play a more important role in daily life. However, how the smartphone impacts our lives need more exploration for it. Based on this background, we will have discuss it from two aspects.

Regarding our first argument, the article provides very valuable insights into the complexity of digital addiction and its impact on individuals and society, urging further research interventions to mitigate its negative effects. The authors discuss and analyze experiments related to subjective well-being. They administered four surveys to participants between April 12th and June 14th. Participants were randomized into rewarding and limiting treatment conditions using an analytic factor design. A participant-led experimental intervention known as the restriction group may have been a part of this. In order to evaluate the impacts of particular digital technology usage patterns on their well-being, experiments estimate treatment effects using regression models that include restriction and reward group indicators. These studies might compare the well-being levels of individuals who use various digital technologies, or they can monitor changes in participants' well-being before and after using digital technology. In research pertaining to mobile phone usage, control and restriction groups can be employed to evaluate the effects of interventions on cell phone use as well as the effects of cell phone use on an individual's behaviour or psychological state.

### 2024-02-13 output/paper.qmd
paper

@@
 In research pertaining to mobile phone usage, control and restriction groups can be employed to evaluate the effects of interventions on cell phone use as well as the effects of cell phone use on an individual's behaviour or psychological state.
+
+#Data
+The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions : - "...I was a happy person." - "...I was satisfied with my I felt anxious." "...I felt depressed." "...I could concentrate on my life." - "...I could concentrate on what I was doing." - "...I was easily distracted." - "...I was easily distracted." - "...
+I slept well." Based on the different responses it is possible to categorize and collect new data.

### 2024-02-13 output/paper.qmd
paper

--- 2024-02-13 output/paper.qmd
@@
 In research pertaining to mobile phone usage, control and restriction groups can be employed to evaluate the effects of interventions on cell phone use as well as the effects of cell phone use on an individual's behaviour or psychological state.
+
+# Data
+The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions : - "...I was a happy person." - "...I was satisfied with my I felt anxious." "...I felt depressed." "...I could concentrate on my life." - "...I could concentrate on what I was doing." - "...I was easily distracted." - "...I was easily distracted." - "...
+I slept well." Based on the different responses it is possible to categorize and collect new data.

### 2024-02-13 output/paper.qmd
paper

--- 2024-02-13 output/paper.qmd
@@
 In research pertaining to mobile phone usage, control and restriction groups can be employed to evaluate the effects of interventions on cell phone use as well as the effects of cell phone use on an individual's behaviour or psychological state.
+
+# Data
+The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions :
+
+* "...I was a happy person." 
+* "...I was satisfied with my I felt anxious." 
+* "...I felt depressed." 
+* "...I could concentrate on my life." 
+* "...I could concentrate on what I was doing." 
+* "...I was easily distracted." 
+* "... I slept well."
+
+Based on the different responses it is possible to categorize and collect new data.

### 2024-02-13 scripts/02-data_cleaning.R
Replicate Figure A4
Previous commit did not catch the replication file

@@ -27,63 +27,124 @@ endline <- as.Date(mdy(yaml_data$metadata$dates$endline))
 daylight_saving_2018 <- as.Date("2018-11-3")
 
 
-# Extract state information from baseline
+# Extract state information from baseline, midline and endline
 raw_baseline <- read_dta("data/raw_data/baseline_anonymous.dta")
+raw_midline <- read_dta("data/raw_data/midline_anonymous.dta")
+raw_endline <- read_dta("data/raw_data/endline_anonymous.dta")
 
+# Clean baseline
+# filter out response that either decide to not continue, or invalid
 cleaned_baseline <- raw_baseline |>
   clean_names() |>
-  filter(consent1 == "Continue")
-  
+  filter(consent1 == "Continue" & fb_minutes < 1440) |>
+  rename(fb_minutes_base = fb_minutes,
+         swb_happiness_base = swb_happiness,
+         swb_relhappiness_base = swb_relhappiness,
+         swb_ideal_base = swb_swl1,
+         swb_conditions_base = swb_swl2,
+         swb_satisfied_base = swb_swl3,
+         swb_lack_companion_base = swb_lnlns1,
+         swb_left_out_base = swb_lnlns2,
+         swb_isolated_base = swb_lnlns3,
+         swb_bored_base = swb_eurhappsvy_4,
+         swb_anxious_base = swb_eurhappsvy_5,
+         swb_depressed_base = swb_eurhappsvy_6,
+         swb_absorbed_worthwhile_base = swb_eurhappsvy_7)
 
-# Fill in missing state abbreviations for individuals who qualified for 
-# the midline but whose Zip codes weren't found
-cleaned_baseline$state[cleaned_baseline$state_prescreen == "Mississippi" & 
-                       cleaned_baseline$state == ""] <- "MS"
-cleaned_baseline$state[cleaned_baseline$state_prescreen == "Wisconsin" & 
-                       cleaned_baseline$state == ""] <- "WI"
-cleaned_baseline$state[cleaned_baseline$state_prescreen == "Utah" & 
-                       cleaned_baseline$state == ""] <- "UT"
-cleaned_baseline$state[cleaned_baseline$state_prescreen == "California" & 
-                       cleaned_baseline$state == ""] <- "CA"
-cleaned_baseline$state[cleaned_baseline$state_prescreen == "Rhode Island" & 
-                       cleaned_baseline$state == ""] <- "RI"
[…]

### 2024-02-13 scripts/99-replications.R

@@ -1,18 +1,82 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... 
-# Author: 
+# Purpose: Replicated graphs from Digital addiction
+# Author: Kenneth Chan, 
 # Date: 11 February 2023 
-# Contact: 
+# Contact: kenchancf0618@gmail.com
 # License: MIT
-# Pre-requisites: 
-# Any other information needed? 
+# Pre-requisites: Digital addiction by Hunt Allcott, Matthew Gentzkow and
+#                 Lena Song
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(dplyr)
 
 #### Load data ####
+social_time <- read_csv("data/analysis_data/social_time.csv",
+                        show_col_types = FALSE)
 
+# Remove extreme cases, make all the social media use time above 800 min to 800.
+social_time <- social_time |>
+  mutate(sum_social_minutes = 
+           ifelse(sum_social_minutes > 800,
+                  800,
+                  sum_social_minutes),
+         fb_minutes =
+           ifelse(fb_minutes > 800,
+                  800,
+                  sum_social_minutes))
+
+###########################################
+### Replicating Figure A4 from appendix ###
+###########################################
+count_participant <- count(social_time)
+# Define breaks for grouping (intervals of 25)
+breaks <- seq(0,
+              ceiling(max(social_time$sum_social_minutes) / 25) * 25,
+              by = 25)
+
+# Prepare the data for graph uses
+graph_data <- social_time |>
+  arrange(sum_social_minutes) |>
+  # Group data into intervals
+  mutate(sum_social_minutes = cut(sum_social_minutes, breaks = breaks)) |>
+  group_by(sum_social_minutes) |>
+  # Calculate the fraction of each interval
+  count(sum_social_minutes) |>
+  mutate(fraction = n / count_participant)
+
+graph_data |>
+  ggplot(aes(x = sum_social_minutes, y = fraction$n)) +
+  geom_bar(stat = "identity", fill = "darkred", width = 1) +
+  scale_x_discrete(label = breaks) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust=0)) +
+  labs(x = "Social media usage (minutes)", y = "Fraction of sample")
+
+# Version with only facebook
[…]

### 2024-02-13 scripts/02-data_cleaning.R
Finish first draft for figure 8

@@ -57,12 +57,12 @@ cleaned_midline <- raw_midline |>
   rename(price1 = first_4weeks_num,
          price2 = second_4weeks_num1) |>
   # Made it to randomization stage in midline
-  mutate(randomized = ifelse(wta_understanding1 == "", 0, 1),
+  mutate(randomized = ifelse(wta_understanding1 == "", FALSE, TRUE),
          # treatment = 1 if price is offered, 0 if not
-         treatment = ifelse(price1 == 102 & wta1 != "" & randomized == 1,
-                            1,
-                            ifelse(price1 == 0 & wta1 != "" & randomized == 1,
-                                   0,
+         treatment = ifelse(price1 == 102 & wta1 != "" & randomized,
+                            TRUE,
+                            ifelse(price1 == 0 & wta1 != "" & randomized,
+                                   FALSE,
                                    NA)))
 
 # Clean endline
@@ -89,6 +89,7 @@ social_time <- cleaned_baseline |>
   # Remove non valid entries
   filter(fb_minutes_base != "")|>
   mutate(fb_minutes_base = as.numeric(fb_minutes_base))
+
 
 # Select variables that are useful for measuring well-being
 # Variables that are useful in baseline
@@ -137,9 +138,99 @@ subjective_well_being <- merge(subjective_well_being,
                                by = "id",
                                all.x = TRUE)
 
+
+# Function for translating response into numeric values
+happiness_numeric <- function(happiness) {
+  recode (happiness,
+          "1 (not a very happy person)" = -3,
+          "2" = -2,
+          "3" = -1,
+          "4" = 0,
+          "5" = 1,
+          "6" = 2,
+          "7 (a very happy person)" = 3,
+          .default = 0
+  )
+}
+
+rel_happiness_numeric <- function(happiness) {
+  recode (happiness,
+          "1 (less happy)" = -3,
+          "2" = -2,
+          "3" = -1,
+          "4" = 0,
+          "5" = 1,
+          "6" = 2,
+          "7 (more happy)" = 3,
+          .default = 0
+  )
+}
+
+swl_numeric <- function(swl) {
+  recode (swl,
+          "Strongly disagree" = -3,
+          "Disagree" = -2,
+          "Slightly disagree" = -1,
[…]

### 2024-02-13 scripts/99-replications.R

@@ -15,6 +15,9 @@ library(tidyverse)
 #### Load data ####
 social_time <- read_csv("data/analysis_data/social_time.csv",
                         show_col_types = FALSE)
+subjective_well_being <- 
+  read_csv("data/analysis_data/subjective_well_being.csv",
+           show_col_types = FALSE)
 
 # Remove extreme cases, make all the social media use time above 800 min to 800.
 social_time <- social_time |>
@@ -80,3 +83,48 @@ graph_data |>
   labs(x = "Facebook usage (minutes)", y = "Fraction of sample")
 
 
+##########################
+### Replicate Figure 8 ###
+##########################
+
+treatment_data <- subjective_well_being |>
+  group_by(treatment) |>
+  reframe(
+    name = c("Happiness",
+             "Relative happiness to peers",
+             "Life is ideal",
+             "Conditions of life is excellent",
+             "Satisfied with life"),
+    mean = c(mean(swb_happiness_base) - mean(swb_happiness_end),
+             mean(swb_relhappiness_base) - mean(swb_relhappiness_end),
+             mean(swb_ideal_base) - mean(swb_ideal_end),
+             mean(swb_conditions_base) - mean(swb_conditions_end),
+             mean(swb_satisfied_base) - mean(swb_satisfied_end)),
+    
+    sd = c(sd(swb_happiness_base - swb_happiness_end)
+           / sqrt(length(subjective_well_being$id)),
+           sd(swb_relhappiness_base - swb_relhappiness_end)
+           / sqrt(length(subjective_well_being$id)),
+           sd(swb_ideal_base - swb_ideal_end)
+           / sqrt(length(subjective_well_being$id)),
+           sd(swb_conditions_base - swb_conditions_end)
+           / sqrt(length(subjective_well_being$id)),
+           sd(swb_satisfied_base - swb_satisfied_end)
+           / sqrt(length(subjective_well_being$id)))
+  ) |>
+  mutate(type = ifelse(treatment, "Treatment", "Control"))
+
+
+
+treatment_data |>
+  ggplot(aes(x = name, y = mean, color = type)) +
+  geom_point(position = position_dodge(width = 0.2)) +
+  geom_errorbar(aes(ymin = mean - 1.96 * sd, ymax = mean + 1.96 * sd),
+                position = position_dodge(width = 0.2),
+                width = 0.1) + 
+  theme_minimal() +
+  ylim(-0.35, 0.35) +
+  coord_flip() +
[…]

### 2024-02-13 scripts/99-replications.R
Tweak to figure 8
change the position for type

@@ -118,9 +118,9 @@ treatment_data <- subjective_well_being |>
 
 treatment_data |>
   ggplot(aes(x = name, y = mean, color = type)) +
-  geom_point(position = position_dodge(width = 0.2)) +
+  geom_point(position = position_dodge(width = -0.2)) +
   geom_errorbar(aes(ymin = mean - 1.96 * sd, ymax = mean + 1.96 * sd),
-                position = position_dodge(width = 0.2),
+                position = position_dodge(width = -0.2),
                 width = 0.1) + 
   theme_minimal() +
   ylim(-0.35, 0.35) +

### 2024-02-13 scripts/02-data_cleaning.R
Update replication graphs

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Cleans the raw data recorded by Hunt Allcot, Luca Braghieri, 
 #          Sarah Eichmeyer and Matthew Gentzkow
-# Author: Kenneth Chan, 
+# Author: Kenneth Chan, Stephanie Xuan Zhao and Siyu Li
 # Date: 11 February 2023 
 # Contact: kenchancf0618@gmail.com
 # License: MIT
@@ -15,16 +15,6 @@ library(haven)
 library(readxl)
 library(janitor)
 library(stringr)
-library(yaml)
-
-# Load the YAML file
-yaml_data <- yaml::yaml.load_file("data/raw_data/config.yaml")
-
-# Access date metadata
-start_experiment <- as.Date(mdy(yaml_data$metadata$dates$start_experiment))
-midline <- as.Date(mdy(yaml_data$metadata$dates$midline))
-endline <- as.Date(mdy(yaml_data$metadata$dates$endline))
-daylight_saving_2018 <- as.Date("2018-11-3")
 
 
 # Extract state information from baseline, midline and endline
@@ -36,7 +26,7 @@ raw_endline <- read_dta("data/raw_data/endline_anonymous.dta")
 # filter out response that either decide to not continue, or invalid
 cleaned_baseline <- raw_baseline |>
   clean_names() |>
-  filter(consent1 == "Continue" & fb_minutes < 1440) |>
+  filter(consent1 == "Continue") |>
   rename(fb_minutes_base = fb_minutes,
          swb_happiness_base = swb_happiness,
          swb_relhappiness_base = swb_relhappiness,
@@ -58,7 +48,7 @@ cleaned_midline <- raw_midline |>
          price2 = second_4weeks_num1) |>
   # Made it to randomization stage in midline
   mutate(randomized = ifelse(wta_understanding1 == "", FALSE, TRUE),
-         # treatment = 1 if price is offered, 0 if not
+         # treatment = TRUE if price is offered, FALSE if not
          treatment = ifelse(price1 == 102 & wta1 != "" & randomized,
                             TRUE,
                             ifelse(price1 == 0 & wta1 != "" & randomized,
@@ -82,18 +72,30 @@ cleaned_endline <- raw_endline |>
          swb_depressed_end = swb_eurhappsvy_6,
          swb_absorbed_worthwhile_end = swb_eurhappsvy_7)
 
+# Clean enviroment
[…]

### 2024-02-13 scripts/99-replications.R

@@ -11,120 +11,229 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(ggpubr)
 
 #### Load data ####
-social_time <- read_csv("data/analysis_data/social_time.csv",
+social_time_data <- 
+  read_csv("data/analysis_data/social_time_data.csv",
                         show_col_types = FALSE)
-subjective_well_being <- 
-  read_csv("data/analysis_data/subjective_well_being.csv",
+subjective_well_being_data <- 
+  read_csv("data/analysis_data/subjective_well_being_data.csv",
+           show_col_types = FALSE)
+treatment_data <- 
+  read_csv("data/analysis_data/treatment_data.csv",
            show_col_types = FALSE)
 
-# Remove extreme cases, make all the social media use time above 800 min to 800.
-social_time <- social_time |>
-  mutate(sum_social_minutes = 
-           ifelse(sum_social_minutes > 800,
-                  800,
-                  sum_social_minutes),
-         fb_minutes =
-           ifelse(fb_minutes > 800,
-                  800,
-                  sum_social_minutes))
+# Combine all data
+all_data <- merge(treatment_data,
+                    merge(social_time_data,
+                          subjective_well_being_data)) |>
+  # filter out non valid response
+  filter(!is.na(treatment)) |>
+  mutate(type = ifelse(treatment, "Treatment", "Control")) |>
+  select(-treatment)
+
+
 
 ###########################################
 ### Replicating Figure A4 from appendix ###
 ###########################################
-count_participant <- count(social_time)
+count_participant <- count(social_time_data)
 # Define breaks for grouping (intervals of 25)
 breaks <- seq(0,
-              ceiling(max(social_time$sum_social_minutes) / 25) * 25,
+              ceiling(800 / 25) * 25,
               by = 25)
 
 # Prepare the data for graph uses
-graph_data <- social_time |>
-  arrange(sum_social_minutes) |>
+graph_data <- all_data |>
+  arrange(fb_minutes_base) |>
   # Group data into intervals
-  mutate(sum_social_minutes = cut(sum_social_minutes, breaks = breaks)) |>
-  group_by(sum_social_minutes) |>
+  mutate(fb_minutes_base = cut(fb_minutes_base, breaks = breaks)) |>
+  group_by(fb_minutes_base, type) |>
[…]

### 2024-02-14 scripts/01-data_cleaning.R
Add test for data
Other changes:
Change directory name,
Add new variable in data cleaning

@@ -67,10 +67,10 @@ cleaned_endline <- raw_endline |>
          swb_lack_companion_end = swb_lnlns1,
          swb_left_out_end = swb_lnlns2,
          swb_isolated_end = swb_lnlns3,
-         swb_bored_end = swb_eurhappsvy_4,
-         swb_anxious_end = swb_eurhappsvy_5,
-         swb_depressed_end = swb_eurhappsvy_6,
-         swb_absorbed_worthwhile_end = swb_eurhappsvy_7)
+         swb_bored_end = swb_eurhappsvy_7,
+         swb_anxious_end = swb_eurhappsvy_4,
+         swb_depressed_end = swb_eurhappsvy_5,
+         swb_absorbed_worthwhile_end = swb_eurhappsvy_6)
 
 # Clean enviroment
 rm(raw_baseline, raw_midline, raw_endline)
@@ -89,9 +89,74 @@ social_time_data <- merge(social_time_data, data) |>
   # Remove non valid entries
   filter(fb_minutes_base != "" & fb_minutes_end != "")|>
   mutate(fb_minutes_base = as.numeric(fb_minutes_base),
-         fb_minutes_end = as.numeric(fb_minutes_end)
+         fb_minutes_end = as.numeric(fb_minutes_end),
+         # Calculate the difference
+         fb_minutes_diff = fb_minutes_end - fb_minutes_base,
          )
 
+
+# Function for translating response into numeric values
+happiness_numeric <- function(happiness) {
+  recode (happiness,
+          "1 (not a very happy person)" = -1,
+          "2" = -2/3,
+          "3" = -1/3,
+          "4" = 0,
+          "5" = 1/3,
+          "6" = 2/3,
+          "7 (a very happy person)" = 1,
+          .default = NaN
+  )
+}
+
+rel_happiness_numeric <- function(happiness) {
+  recode (happiness,
+          "1 (less happy)" = -1,
+          "2" = -2/3,
+          "3" = -1/3,
+          "4" = 0,
+          "5" = 1/3,
+          "6" = 2/3,
+          "7 (more happy)" = 1,
+          .default = NaN
+  )
+}
+
+swl_numeric <- function(swl) {
+  recode (swl,
+          "Strongly disagree" = -1,
+          "Disagree" = -2/3,
+          "Slightly disagree" = -1/3,
+          "Neither agree nor disagree" = 0,
+          "Slightly agree" = 1/3,
+          "Agree" = 2/3,
+          "Strongly agree" = 1,
+          .default = NaN
+  )
[…]

### 2024-02-14 scripts/02-test_data.R

@@ -1,0 +1,50 @@
+#### Preamble ####
+# Purpose: Tests... 
+# Author: 
+# Date: 11 February 2023 
+# Contact: 
+# License: MIT
+# Pre-requisites: 
+# Any other information needed? 
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Test data ####
+### subjective well being test ###
+subjective_well_being_data <- 
+  read_csv("data/analysis_data/subjective_well_being_data.csv",
+           show_col_types = FALSE)
+
+# Every ideal is in category
+subjective_well_being_data |>
+  select(swb_ideal_end) |>
+  arrange(swb_ideal_end) |>
+  distinct() == c(-1, -2/3, -1/3, 0, 1/3, 2/3, 1)
+
+all(subjective_well_being_data$swb_social_index_diff ==
+      subjective_well_being_data$swb_social_index_end -
+      subjective_well_being_data$swb_social_index_base)
+
+### Treatment data test ###
+treatment_data <- read_csv("data/analysis_data/treatment_data.csv",
+                           show_col_types = FALSE)
+
+# There are some respondent are not in any group
+treatment_data |>
+  select(treatment) |>
+  arrange(treatment) |>
+  distinct() == c(FALSE, TRUE)
+
+### Social time data test ###
+social_time_data <- read_csv("data/analysis_data/social_time_data.csv",
+                             show_col_types = FALSE)
+
+all(social_time_data$fb_minutes_base >= 0)
+
+all(social_time_data$fb_minutes_end >= 0)
+
+all(social_time_data$fb_minutes_diff ==
+      social_time_data$fb_minutes_end -
+      social_time_data$fb_minutes_base)

### 2024-02-14 scripts/03-test_data.R

@@ -1,15 +1,0 @@
-#### Preamble ####
-# Purpose: Tests... 
-# Author: 
-# Date: 11 February 2023 
-# Contact: 
-# License: MIT
-# Pre-requisites: 
-# Any other information needed? 
-
-
-#### Workspace setup ####
-library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Test data ####

### 2024-02-14 scripts/99-replications.R

@@ -114,91 +114,85 @@ graph_data <- all_data |>
       "Bored",
       "Anxious",
       "Depressed",
-      "Absorbed in doing something worthwhile",
-      "Feeling index"
+      "Absorbed in doing something worthwhile"
       ),
-    mean = c(mean(fb_minutes_end - fb_minutes_base)
+    mean = c(mean(fb_minutes_diff)
              / sd(fb_minutes_base),
-             mean(swb_happiness_end - swb_happiness_base)
+             mean(swb_happiness_diff)
              / sd(swb_happiness_base),
-             mean(swb_relhappiness_end - swb_relhappiness_base)
+             mean(swb_relhappiness_diff)
              / sd(swb_relhappiness_base),
-             mean(swb_ideal_end - swb_ideal_base)
+             mean(swb_ideal_diff)
              / sd(swb_ideal_base),
-             mean(swb_conditions_end - swb_conditions_base)
+             mean(swb_conditions_diff)
              / sd(swb_conditions_base),
-             mean(swb_satisfied_end - swb_satisfied_base)
+             mean(swb_satisfied_diff)
              / sd(swb_satisfied_base),
-             mean(swb_wellbeing_index_end - swb_wellbeing_index_base)
+             mean(swb_wellbeing_index_diff)
              / sd(swb_wellbeing_index_base),
-             mean(swb_lack_companion_end - swb_lack_companion_base)
+             mean(swb_lack_companion_diff)
              / sd(swb_lack_companion_base),
-             mean(swb_left_out_end - swb_left_out_base)
+             mean(swb_left_out_diff)
              / sd(swb_left_out_base),
-             mean(swb_isolated_end - swb_isolated_base)
+             mean(swb_isolated_diff)
              / sd(swb_isolated_base),
-             mean(swb_social_index_end - swb_social_index_base)
+             mean(swb_social_index_diff)
              / sd(swb_social_index_base),
-             mean(swb_bored_end - swb_bored_base)
+             mean(swb_bored_diff)
              / sd(swb_bored_base),
-             mean(swb_anxious_end - swb_anxious_base)
+             mean(swb_anxious_diff)
              / sd(swb_anxious_base),
-             mean(swb_depressed_end - swb_depressed_base)
+             mean(swb_depressed_diff)
              / sd(swb_depressed_base),
[…]

### 2024-02-14 scripts/01-data_cleaning.R
Add figure 3

@@ -28,6 +28,7 @@ cleaned_baseline <- raw_baseline |>
   clean_names() |>
   filter(consent1 == "Continue") |>
   rename(fb_minutes_base = fb_minutes,
+         # Subjective wellness being
          swb_happiness_base = swb_happiness,
          swb_relhappiness_base = swb_relhappiness,
          swb_ideal_base = swb_swl1,
@@ -39,7 +40,9 @@ cleaned_baseline <- raw_baseline |>
          swb_bored_base = swb_eurhappsvy_4,
          swb_anxious_base = swb_eurhappsvy_5,
          swb_depressed_base = swb_eurhappsvy_6,
-         swb_absorbed_worthwhile_base = swb_eurhappsvy_7)
+         swb_absorbed_worthwhile_base = swb_eurhappsvy_7,
+         # Facebook opinion
+         fb_soclife_base = fb_soclife_1)
 
 # Clean midline
 cleaned_midline <- raw_midline |>
@@ -59,6 +62,7 @@ cleaned_midline <- raw_midline |>
 cleaned_endline <- raw_endline |>
   clean_names() |>
   rename(fb_minutes_end = fb_minutes,
+         # Subjective wellness being
          swb_happiness_end = swb_happiness,
          swb_relhappiness_end = swb_relhappiness,
          swb_ideal_end = swb_swl1,
@@ -70,7 +74,9 @@ cleaned_endline <- raw_endline |>
          swb_bored_end = swb_eurhappsvy_7,
          swb_anxious_end = swb_eurhappsvy_4,
          swb_depressed_end = swb_eurhappsvy_5,
-         swb_absorbed_worthwhile_end = swb_eurhappsvy_6)
+         swb_absorbed_worthwhile_end = swb_eurhappsvy_6,
+         # Facebook opinion
+         fb_soclife_end = fb_soclife_1)
 
 # Clean enviroment
 rm(raw_baseline, raw_midline, raw_endline)
@@ -160,7 +166,7 @@ feel_numeric <- function(feel) {
 
 # Select variables that are useful for measuring well-being
 # Variables that are useful in baseline
-subjective_well_being_data <- cleaned_baseline |>
+data1 <- cleaned_baseline |>
   select(id,
          swb_happiness_base,
          swb_relhappiness_base,
@@ -176,7 +182,7 @@ subjective_well_being_data <- cleaned_baseline |>
          swb_absorbed_worthwhile_base)
 
[…]

### 2024-02-14 scripts/02-test_data.R

@@ -48,3 +48,6 @@ all(social_time_data$fb_minutes_end >= 0)
 all(social_time_data$fb_minutes_diff ==
       social_time_data$fb_minutes_end -
       social_time_data$fb_minutes_base)
+
+# Clean environment
+rm(list = ls())

### 2024-02-14 scripts/99-replications.R

@@ -24,10 +24,15 @@ treatment_data <-
   read_csv("data/analysis_data/treatment_data.csv",
            show_col_types = FALSE)
 
+opinion_data <- 
+  read_csv("data/analysis_data/opinion_data.csv",
+           show_col_types = FALSE)
+
 # Combine all data
-all_data <- merge(treatment_data,
-                    merge(social_time_data,
-                          subjective_well_being_data)) |>
+all_data <- merge(opinion_data,
+            merge(treatment_data,
+            merge(social_time_data,
+                  subjective_well_being_data))) |>
   # filter out non valid response
   filter(!is.na(treatment)) |>
   mutate(type = ifelse(treatment, "Treatment", "Control")) |>
@@ -35,10 +40,11 @@ all_data <- merge(treatment_data,
 
 
 
+
 ###########################################
 ### Replicating Figure A4 from appendix ###
 ###########################################
-count_participant <- count(social_time_data)
+count_participant <- count(all_data)
 # Define breaks for grouping (intervals of 25)
 breaks <- seq(0,
               ceiling(800 / 25) * 25,
@@ -92,9 +98,9 @@ ggarrange(
 )
 
 
-##########################
-### Replicate Figure 8 ###
-##########################
+##########################################
+### Replicate bottom right of Figure 8 ###
+##########################################
 
 graph_data <- all_data |>
   group_by(type) |>
@@ -225,6 +231,54 @@ graph_data |>
   labs(y = "Difference from baseline (standard deviation)",
      x = "Subjective wellness being",
      color = "Type")
+
+##########################
+### Replicate Figure 3 ###
+##########################
+count_participant <- count(all_data)
+
+# Prepare the data for graph uses
+graph_data <- all_data |>
+  arrange(fb_soclife_base) |>
+  group_by(fb_soclife_base, type) |>
+  # Calculate the fraction of each interval
+  count(fb_soclife_base) |>
+  mutate(fraction = n / count_participant)
+
+fig3a <- graph_data |>
+  ggplot(aes(x = fb_soclife_base, y = fraction$n, fill = type)) +
+  geom_bar(stat = "identity", width = 1) +
+  theme_minimal() +
+  labs(title = "Baseline",
+       x = "Facebook usage make social life worse(left)
+       or better (right)",
+       y = "Fraction of sample",
+       fill = "Type")
+
+
[…]

### 2024-02-15 scripts/01-data_cleaning.R
Add two graphs
Fraction of liberal or conservative, and democrats or Democrat

@@ -14,7 +14,6 @@ library(tidyverse)
 library(haven)
 library(readxl)
 library(janitor)
-library(stringr)
 
 
 # Extract state information from baseline, midline and endline
@@ -309,6 +308,37 @@ opinion_data <- merged_data |>
   mutate(fb_soclife_base = as.numeric(fb_soclife_base) - 5,
          fb_soclife_end = as.numeric(fb_soclife_end) - 5,
          fb_soclife_diff = fb_soclife_end - fb_soclife_base)
+
+
+# Select variables that are useful for political opinions
+political_numeric <- function(feel) {
+  recode (feel,
+          "1. None or almost none of the time" = -1,
+          "1. None or almost none of the times" = -1,
+          "2" = -1/3,
+          "2." = -1/3,
+          "3" = 1/3,
+          "3." = 1/3,
+          "4. All or almost all of the time" = 1,
+          "4. All or almost all of the time." = 1,
+          .default = NaN
+  )
+}
+# Variables that are useful in baseline
+data1 <- cleaned_baseline |>
+  select(id,
+         repdem, 
+         libcon)
+
+# Variables that are useful in endline
+data2 <- cleaned_endline |>
+  select(id)
+
+merged_data <- merge(data1, data2, by = "id", all.x = TRUE)
+
+political_data <- merged_data |>
+  filter(repdem != "",
+         libcon != "")
   
 
 #### Save data ####
@@ -320,6 +350,8 @@ write_csv(treatment_data,
           "data/analysis_data/treatment_data.csv")
 write_csv(opinion_data,
           "data/analysis_data/opinion_data.csv")
+write_csv(political_data,
+          "data/analysis_data/political_data.csv")
 
 # Clean environment
 rm(list = ls())

### 2024-02-15 scripts/99-replications.R

@@ -28,11 +28,16 @@ opinion_data <-
   read_csv("data/analysis_data/opinion_data.csv",
            show_col_types = FALSE)
 
+political_data <-
+  read_csv("data/analysis_data/political_data.csv",
+           show_col_types = FALSE)
+
 # Combine all data
-all_data <- merge(opinion_data,
+all_data <- merge(political_data,
+            merge(opinion_data,
             merge(treatment_data,
             merge(social_time_data,
-                  subjective_well_being_data))) |>
+                  subjective_well_being_data)))) |>
   # filter out non valid response
   filter(!is.na(treatment)) |>
   mutate(type = ifelse(treatment, "Treatment", "Control")) |>
@@ -93,8 +98,7 @@ fig8b <- graph_data |>
        fill = "Type")
 
 ggarrange(
-  fig8a, fig8b, nrow = 2,
-  common.legend = TRUE, legend = "bottom"
+  fig8a, fig8b, nrow = 2, common.legend = TRUE, legend = "bottom"
 )
 
 
@@ -117,10 +121,11 @@ graph_data <- all_data |>
       "Feeling left out",
       "Feel isolated",
       "Social index",
-      "Bored",
-      "Anxious",
-      "Depressed",
-      "Absorbed in doing something worthwhile"
+      "Bored(-1)",
+      "Anxious(-1)",
+      "Depressed(-1)",
+      "Absorbed in doing something worthwhile",
+      "Feeling index"
       ),
     mean = c(mean(fb_minutes_diff)
              / sd(fb_minutes_base),
@@ -144,14 +149,16 @@ graph_data <- all_data |>
              / sd(swb_isolated_base),
              mean(swb_social_index_diff)
              / sd(swb_social_index_base),
-             mean(swb_bored_diff)
+             - mean(swb_bored_diff)
              / sd(swb_bored_base),
-             mean(swb_anxious_diff)
+             - mean(swb_anxious_diff)
              / sd(swb_anxious_base),
-             mean(swb_depressed_diff)
+             - mean(swb_depressed_diff)
              / sd(swb_depressed_base),
              mean(swb_absorbed_worthwhile_diff)
-             / sd(swb_absorbed_worthwhile_base)
+             / sd(swb_absorbed_worthwhile_base),
+             - mean(swb_feeling_index_diff)
+             / sd(swb_feeling_index_base)
             ),
     
     sd = c(sd(fb_minutes_diff)
[…]

### 2024-02-15 scripts/01-data_cleaning.R
Add figure for political opinions

@@ -83,14 +83,14 @@ rm(raw_baseline, raw_midline, raw_endline)
 
 # Select variables that are useful for measuring social media usage
 # Variables that are useful in baseline
-social_time_data <- cleaned_baseline |>
+data1 <- cleaned_baseline |>
   select(id, fb_minutes_base)
 
 # Variables that are useful in endline
-data <- cleaned_endline |>
+data2 <- cleaned_endline |>
   select(id, fb_minutes_end)
 
-social_time_data <- merge(social_time_data, data) |>
+social_time_data <- merge(data1, data2) |>
   # Remove non valid entries
   filter(fb_minutes_base != "" & fb_minutes_end != "")|>
   mutate(fb_minutes_base = as.numeric(fb_minutes_base),
@@ -100,7 +100,7 @@ social_time_data <- merge(social_time_data, data) |>
          )
 
 
-# Function for translating response into numeric values
+# Functions for cleaning well-being response
 happiness_numeric <- function(happiness) {
   recode (happiness,
           "1 (not a very happy person)" = -1,
@@ -178,35 +178,8 @@ data1 <- cleaned_baseline |>
          swb_bored_base,
          swb_anxious_base,
          swb_depressed_base,
-         swb_absorbed_worthwhile_base)
-
-# Variables that are useful in endline
-data2 <- cleaned_endline |>
-  select(id,
-         swb_happiness_end,
-         swb_relhappiness_end,
-         swb_ideal_end,
-         swb_conditions_end,
-         swb_satisfied_end,
-         swb_lack_companion_end,
-         swb_left_out_end,
-         swb_isolated_end,
-         swb_bored_end,
-         swb_anxious_end,
-         swb_depressed_end,
-         swb_absorbed_worthwhile_end)
-
-merged_data <- merge(data1, data2, by = "id", all.x = TRUE)
-
-# Distinguish treatment and control
-treatment_data <- cleaned_midline |>
-  select(id, treatment)
-
-
-
-subjective_well_being_data <- merged_data |>
-  # Translate the response to numeric
-  mutate(# Baseline responses
+         swb_absorbed_worthwhile_base) |>
+  mutate(# Translate the response to numeric
     swb_happiness_base = happiness_numeric(swb_happiness_base),
     swb_relhappiness_base = rel_happiness_numeric(swb_relhappiness_base),
[…]

### 2024-02-15 scripts/02-test_data.R

@@ -49,5 +49,7 @@ all(social_time_data$fb_minutes_diff ==
       social_time_data$fb_minutes_end -
       social_time_data$fb_minutes_base)
 
+# max(political_data$feeling_dem_base)
+
 # Clean environment
 rm(list = ls())

### 2024-02-15 scripts/99-replications.R

@@ -345,6 +345,85 @@ graph_data |>
   coord_flip()
 
 
+### Political dot plot ###
+
+graph_data <- all_data |>
+  mutate(party = 
+           recode(
+             repdem,
+             "Democrat (Strongly Democratic)" = "Democrat",
+             "Democrat (Weakly Democratic)" = "Democrat",
+             "Independent (Lean toward the Democratic Party)" = "Independent",
+             "Independent (Lean toward the Republican Party)" = "Independent",
+             "Republican (Weakly Republican)" = "Republican",
+             "Republican (Strongly Republican)" = "Republican",
+           )) |>
+  group_by(party) |>
+  reframe(
+    name = c(
+      "Feeling towards Democratic
+    Cold (left) or Warm (right)",
+      "Feeling towards Republican
+    Cold (left) or Warm (right)",
+      "Feeling towards Trump
+    Cold (left) or Warm (right)",
+      "Understand Democratic POV",
+      "Understand Republican POV"
+    ),
+    mean = c(mean(feeling_dem_diff)
+             / sd(feeling_dem_base),
+             mean(feeling_rep_diff)
+             / sd(feeling_rep_base),
+             mean(feeling_trump_diff)
+             / sd(feeling_trump_base),
+             mean(rep_pov_diff)
+             / sd(rep_pov_base),
+             mean(dem_pov_diff)
+             / sd(dem_pov_base)
+    ),
+    
+    sd = c(sd(feeling_dem_diff)
+           / sqrt(length(id))
+           / sd(feeling_dem_base),
+           sd(feeling_rep_diff)
+           / sqrt(length(id))
+           / sd(feeling_rep_base),
+           sd(feeling_trump_diff)
+           / sqrt(length(id))
+           / sd(feeling_trump_base),
+           sd(rep_pov_diff)
+           / sqrt(length(id))
+           / sd(rep_pov_base),
+           sd(dem_pov_diff)
+           / sqrt(length(id))
+           / sd(dem_pov_base)
+    )
+  ) |>
+  mutate(name = factor(name, rev(c(
+    "Feeling towards Democratic
+    Cold (left) or Warm (right)",
+    "Feeling towards Republican
+    Cold (left) or Warm (right)",
+    "Feeling towards Trump
+    Cold (left) or Warm (right)",
+    "Understand Democratic POV",
+    "Understand Republican POV"
+  ))))
+
+
+graph_data |>
[…]

### 2024-02-15 output/paper.qmd
paper
try import data into paper

@@
 #| message: false
+
+#install.packages("tidyverse")
+#install.packages("haven")
+#install.packages("readxl")
+#install.packages("janitor")
+#install.packages("ggpubr")
+
+library(tidyverse)
+library(haven)
+library(readxl)
+library(janitor)
+library(ggpubr)
+
+setwd("..")
+#### Import Data ####
+#### Explore ####
+dinesafe_program_clean <-
+  read_csv(
+   here::here("scripts/02_data_cleaning.R"),
+    show_col_types = FALSE
+  )
 
@@
 Based on the different responses it is possible to categorize and collect new data.
+
+# Result
+
+# Discuss
+
+# Reference

### 2024-02-15 paper/paper.qmd
import data

--- 2024-02-15 output/paper.qmd
@@
 #### Explore ####
-dinesafe_program_clean <-
+digital_clean_data <-
   read_csv(

### 2024-02-15 paper/paper.qmd
add result part

@@
 # Result
+Figure 1
+It shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
+In this graph, the x-axis is the difference from the baseline, the y-axis is the subjective well-being, the orange line is the control group, the blue line is the treatment group, and the confidence interval is 95%.
+The treatment group was controlled by the researcher for the amount of time spent on Facebook per day and was rewarded accordingly for being controlled.
+The research target also generally responded that receiving the reward mechanism could greatly improve their subjective well-being.
+In contrast, there was not much change in the other survey directions.
+From the figure we can also see that the difference between the values of happiness, and conditions of life is excellent is not big, they are all concentrated in the range of -0.25 to 0.25.
+The subjective happiness of the treatment group will be a little bit lower than that of the control group at this time.
+
+Figure 2
+These two figures show the distribution of Facebook usage at Baseline and Endline.
+The red is the control group and the green is the treatment group.
+The Y-axis shows the fraction of the sample and the x-axis shows Facebook usage time.
+For the longest time, the endline group’s time is shorter than the baseline’s time and the longest time both happen in the control group.
+The longest time for the treatment group is 550 minutes in baseline and 450 minutes in the endline group.
+For the treatment group, it decreases from 625 minutes to 575 minutes.
+To this result, there is a large decrease for the longest usage time.
+For the baseline, usage time exceeding 250 minutes is more than 2.5% in total but compared with it, at the endline, for the control group it has around 5% and for treatment is only 1.25%.
+
+It is obvious that between 0 and 125 minutes, the figure has a skew left and generally fraction decreases for each period in the treatment group.
+
+Figure 3
+The above two figures show whether Facebook usage makes social life worse or better.
+The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale.
+From the figure, it has changed between -1 and 1.
+At baseline, it has the most fraction at 0 for the treatment group and in the control group, it has the most in -1 and 0.
+However, in endline’s figure, the biggest fraction shifts to the right.
+It becomes 0 and 1.
+This means that user feels their social life becomes better.
+
+Figure 4
 

### 2024-02-15 paper/paper.qmd
Add figure in paper.qmd

@@
 
-#install.packages("tidyverse")
-#install.packages("haven")
-#install.packages("readxl")
-#install.packages("janitor")
-#install.packages("ggpubr")
-
+#### Workspace setup ####
 library(tidyverse)
@@
 setwd("..")
-#### Import Data ####
-#### Explore ####
-digital_clean_data <-
-  read_csv(
-   here::here("scripts/02_data_cleaning.R"),
-    show_col_types = FALSE
-  )
+
+#### Load data ####
+social_time_data <- 
+  read_csv("data/analysis_data/social_time_data.csv",
+                        show_col_types = FALSE)
+subjective_well_being_data <- 
+  read_csv("data/analysis_data/subjective_well_being_data.csv",
+           show_col_types = FALSE)
+treatment_data <- 
+  read_csv("data/analysis_data/treatment_data.csv",
+           show_col_types = FALSE)
+
+opinion_data <- 
+  read_csv("data/analysis_data/opinion_data.csv",
+           show_col_types = FALSE)
+
+political_data <-
+  read_csv("data/analysis_data/political_data.csv",
+           show_col_types = FALSE)
+
+# Combine all data
+all_data <- merge(political_data,
+            merge(opinion_data,
+            merge(treatment_data,
+            merge(social_time_data,
+                  subjective_well_being_data)))) |>
+  # filter out non valid response
+  filter(!is.na(treatment)) |>
+  mutate(type = ifelse(treatment, "Treatment", "Control")) |>
+  select(-treatment)
 
@@
 # Introduction
+
 In 2023, there will be more than 4.95 billion users of different social media across the world.
@@
 # Data
+
 The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions :
 
-* "...I was a happy person." 
-* "...I was satisfied with my I felt anxious." 
-* "...I felt depressed." 
-* "...I could concentrate on my life." 
-* "...I could concentrate on what I was doing." 
-* "...I was easily distracted." 
-* "... I slept well."
+-   "...I was a happy person."
+-   "...I was satisfied with my I felt anxious."
+-   "...I felt depressed."
+-   "...I could concentrate on my life."
+-   "...I could concentrate on what I was doing."
+-   "...I was easily distracted."
+-   "... I slept well."
 
@@
 
+```{r}
+#| label: fig-1
+#| fig-cap: figure 1 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+count_participant <- count(all_data)
+# Define breaks for grouping (intervals of 25)
+breaks <- seq(0,
+              ceiling(800 / 25) * 25,
+              by = 25)
+
+# Prepare the data for graph uses
+graph_data <- all_data |>
+  arrange(fb_minutes_base) |>
+  # Group data into intervals
+  mutate(fb_minutes_base = cut(fb_minutes_base, breaks = breaks)) |>
+  group_by(fb_minutes_base, type) |>
+  # Calculate the fraction of each interval
+  count(fb_minutes_base) |>
+  mutate(fraction = n / count_participant) |>
+  filter(!is.na(fb_minutes_base))
+
+fig8a <- graph_data |>
+  ggplot(aes(x = fb_minutes_base, y = fraction$n, fill = type)) +
+  geom_bar(stat = "identity", width = 1) +
+  scale_x_discrete(label = breaks) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust=0)) +
+  labs(x = "Baseline Facebook usage (minutes)",
+       y = "Fraction of sample",
+       fill = "Type")
+
+# end version
+graph_data <- all_data |>
+  arrange(fb_minutes_end) |>
+  # Group data into intervals
+  mutate(fb_minutes_end = cut(fb_minutes_end, breaks = breaks)) |>
+  group_by(fb_minutes_end, type) |>
+  # Calculate the fraction of each interval
+  count(fb_minutes_end) |>
+  mutate(fraction = n / count_participant) |>
+  filter(!is.na(fb_minutes_end))
+
+fig8b <- graph_data |>
+  ggplot(aes(x = fb_minutes_end, y = fraction$n, fill = type)) +
+  geom_bar(stat = "identity", width = 1) +
+  scale_x_discrete(label = breaks) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust=0)) +
+  labs(x = "Endline Facebook usage (minutes)",
+       y = "Fraction of sample",
+       fill = "Type")
+
+ggarrange(
+  fig8a, fig8b, nrow = 2, common.legend = TRUE, legend = "bottom"
+)
+```
+
+```{r}
+#| label: fig-2
+#| fig-cap: figure 2 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+graph_data <- all_data |>
+  group_by(type) |>
+  reframe(
+    name = c(
+      "Facebook minutes",
+      "Happiness",
+      "Relative happiness to peers",
+      "Life is ideal",
+      "Conditions of life is excellent",
+      "Satisfied with life",
+      "Well being index",
+      "Lack companion",
+      "Feeling left out",
+      "Feel isolated",
+      "Social index",
+      "Bored(-1)",
+      "Anxious(-1)",
+      "Depressed(-1)",
+      "Absorbed in doing something worthwhile",
+      "Feeling index"
+      ),
+    mean = c(mean(fb_minutes_diff)
+             / sd(fb_minutes_base),
+             mean(swb_happiness_diff)
+             / sd(swb_happiness_base),
+             mean(swb_relhappiness_diff)
+             / sd(swb_relhappiness_base),
+             mean(swb_ideal_diff)
+             / sd(swb_ideal_base),
+             mean(swb_conditions_diff)
+             / sd(swb_conditions_base),
+             mean(swb_satisfied_diff)
+             / sd(swb_satisfied_base),
+             mean(swb_wellbeing_index_diff)
+             / sd(swb_wellbeing_index_base),
+             mean(swb_lack_companion_diff)
+             / sd(swb_lack_companion_base),
+             mean(swb_left_out_diff)
+             / sd(swb_left_out_base),
+             mean(swb_isolated_diff)
+             / sd(swb_isolated_base),
+             mean(swb_social_index_diff)
+             / sd(swb_social_index_base),
+             - mean(swb_bored_diff)
+             / sd(swb_bored_base),
+             - mean(swb_anxious_diff)
+             / sd(swb_anxious_base),
+             - mean(swb_depressed_diff)
+             / sd(swb_depressed_base),
+             mean(swb_absorbed_worthwhile_diff)
+             / sd(swb_absorbed_worthwhile_base),
+             - mean(swb_feeling_index_diff)
+             / sd(swb_feeling_index_base)
+            ),
+
+    sd = c(sd(fb_minutes_diff)
+           / sqrt(length(id))
+           / sd(fb_minutes_base),
+           sd(swb_happiness_diff)
+           / sqrt(length(id))
+           / sd(swb_happiness_base),
+           sd(swb_relhappiness_diff)
+           / sqrt(length(id))
+           / sd(swb_relhappiness_base),
+           sd(swb_ideal_diff)
+           / sqrt(length(id))
+           / sd(swb_ideal_base),
+           sd(swb_conditions_diff)
+           / sqrt(length(id))
+           / sd(swb_conditions_base),
+           sd(swb_satisfied_diff)
+           / sqrt(length(id))
+           / sd(swb_satisfied_base),
+           sd(swb_wellbeing_index_diff)
+           / sqrt(length(id))
+           / sd(swb_wellbeing_index_base),
+           sd(swb_lack_companion_diff)
+           / sqrt(length(id))
+           / sd(swb_lack_companion_base),
+           sd(swb_left_out_diff)
+           / sqrt(length(id))
+           / sd(swb_left_out_base),
+           sd(swb_isolated_diff)
+           / sqrt(length(id))
+           / sd(swb_isolated_base),
+           sd(swb_social_index_diff)
+           / sqrt(length(id))
+           / sd(swb_social_index_base),
+           sd(swb_bored_diff)
+           / sqrt(length(id))
+           / sd(swb_bored_base),
+           sd(swb_anxious_diff)
+           / sqrt(length(id))
+           / sd(swb_anxious_base),
+           sd(swb_depressed_diff)
+           / sqrt(length(id))
+           / sd(swb_depressed_base),
+           sd(swb_absorbed_worthwhile_diff)
+           / sqrt(length(id))
+           / sd(swb_absorbed_worthwhile_base),
+           sd(swb_feeling_index_diff)
+           / sqrt(length(id))
+           / sd(swb_feeling_index_base)
+           )
+  ) |>
+  mutate(name = factor(name, rev(c(
+           "Facebook minutes",
+           "Happiness",
+           "Relative happiness to peers",
+           "Life is ideal",
+           "Conditions of life is excellent",
+           "Satisfied with life",
+           "Well being index",
+           "Lack companion",
+           "Feeling left out",
+           "Feel isolated",
+           "Social index",
+           "Bored(-1)",
+           "Anxious(-1)",
+           "Depressed(-1)",
+           "Absorbed in doing something worthwhile",
+           "Feeling index"
+           ))))
+
+graph_data |>
+  ggplot(aes(x = name, y = mean, color = type)) +
+  geom_point(position = position_dodge(width = -0.2)) +
+  geom_errorbar(aes(ymin = mean - abs(1.96 * sd), ymax = mean + abs(1.96 * sd)),
+                position = position_dodge(width = -0.2),
+                width = 0.2) + 
+  geom_hline(yintercept = 0) +
+  theme_minimal() +
+  coord_flip(expand = TRUE) +
+  labs(y = "Difference from baseline (standard deviation)",
+     x = "Subjective wellness being",
+     color = "Type")
+```
+
+```{r}
+#| label: fig-3
+#| fig-cap: figure 3 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+count_participant <- count(all_data)
+
+# Prepare the data for graph uses
+graph_data <- all_data |>
+  arrange(fb_soclife_base) |>
+  group_by(fb_soclife_base, type) |>
+  # Calculate the fraction of each interval
+  count(fb_soclife_base) |>
+  mutate(fraction = n / count_participant)
+
+fig3a <- graph_data |>
+  ggplot(aes(x = fb_soclife_base, y = fraction$n, fill = type)) +
+  geom_bar(stat = "identity", width = 1) +
+  theme_minimal() +
+  labs(title = "Baseline",
+       x = "Facebook usage make social life worse(left)
+       or better (right)",
+       y = "Fraction of sample",
+       fill = "Type")
+
+# end version
+graph_data <- all_data |>
+  arrange(fb_soclife_end) |>
+  group_by(fb_soclife_end, type) |>
+  # Calculate the fraction of each interval
+  count(fb_soclife_end) |>
+  mutate(fraction = n / count_participant)
+
+fig3b <- graph_data |>
+  ggplot(aes(x = fb_soclife_end, y = fraction$n, fill = type)) +
+  geom_bar(stat = "identity", width = 1) +
+  theme_minimal() +
+  labs(title = "Endline",
+       x = "Facebook usage make social life worse (left)
+       or better (right)",
+       y = "Fraction of sample",
+       fill = "Type")
+
+ggarrange(
+  fig3a, fig3b, nrow = 2, common.legend = TRUE, legend = "bottom"
+)
+
+```
+
+```{r}
+#| label: fig-4
+#| fig-cap: figure 4 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+count_participant <- count(all_data)
+
+### Distribution of republican, democrat and independent ###
+graph_data <- all_data |>
+  group_by(repdem) |>
+  # Calculate the fraction of each interval
+  count(repdem) |>
+  mutate(fraction = n / count_participant,
+         repdem = factor(repdem, c(
+           "Democrat (Strongly Democratic)",
+           "Democrat (Weakly Democratic)",
+           "Independent (Lean toward the Democratic Party)",
+           "Independent",
+           "Independent (Lean toward the Republican Party)",
+           "Republican (Weakly Republican)",
+           "Republican (Strongly Republican)"
+         )))
+
+graph_data |>
+  ggplot(aes(x = repdem, y = fraction$n)) +
+  geom_bar(stat = "identity", fill = "darkred") +
+  theme_minimal() +
+  labs(x = "Republican, Democrat or Independent",
+       y = "Fraction of sample") +
+  coord_flip()
+```
+
+```{r}
+#| label: fig-5
+#| fig-cap: figure 5 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+### Distribution of liberal and conservative ###
+
+graph_data <- all_data |>
+  group_by(libcon) |>
+  # Calculate the fraction of each interval
+  count(libcon) |>
+  mutate(fraction = n / count_participant,
+         libcon = factor(libcon, c(
+           "Extremely liberal",
+           "Liberal",
+           "Slightly liberal",
+           "Moderate",
+           "Slightly conservative",
+           "Conservative",
+           "Extremely conservative"
+         )))
+
+graph_data |>
+  ggplot(aes(x = libcon, y = fraction$n)) +
+  geom_bar(stat = "identity", fill = "darkred") +
+  theme_minimal() +
+  labs(x = "Liberal or Conservative",
+       y = "Fraction of sample") +
+  coord_flip()
+```
+
+```{r}
+#| label: fig-6
+#| fig-cap: figure 6 cap
+#| echo: false
+#| warning: false
+#| message: false
+
+### Political dot plot ###
+
+graph_data <- all_data |>
+  mutate(party = 
+           recode(
+             repdem,
+             "Democrat (Strongly Democratic)" = "Democrat",
+             "Democrat (Weakly Democratic)" = "Democrat",
+             "Independent (Lean toward the Democratic Party)" = "Independent",
+             "Independent (Lean toward the Republican Party)" = "Independent",
+             "Republican (Weakly Republican)" = "Republican",
+             "Republican (Strongly Republican)" = "Republican",
+           )) |>
+  group_by(party) |>
+  reframe(
+    name = c(
+      "Feeling towards Democratic
+    Cold (left) or Warm (right)",
+      "Feeling towards Republican
+    Cold (left) or Warm (right)",
+      "Feeling towards Trump
+    Cold (left) or Warm (right)",
+      "Understand Democratic POV",
+      "Understand Republican POV"
+    ),
+    mean = c(mean(feeling_dem_diff)
+             / sd(feeling_dem_base),
+             mean(feeling_rep_diff)
+             / sd(feeling_rep_base),
+             mean(feeling_trump_diff)
+             / sd(feeling_trump_base),
+             mean(rep_pov_diff)
+             / sd(rep_pov_base),
+             mean(dem_pov_diff)
+             / sd(dem_pov_base)
+    ),
+
+    sd = c(sd(feeling_dem_diff)
+           / sqrt(length(id))
+           / sd(feeling_dem_base),
+           sd(feeling_rep_diff)
+           / sqrt(length(id))
+           / sd(feeling_rep_base),
+           sd(feeling_trump_diff)
+           / sqrt(length(id))
+           / sd(feeling_trump_base),
+           sd(rep_pov_diff)
+           / sqrt(length(id))
+           / sd(rep_pov_base),
+           sd(dem_pov_diff)
+           / sqrt(length(id))
+           / sd(dem_pov_base)
+    )
+  ) |>
+  mutate(name = factor(name, rev(c(
+    "Feeling towards Democratic
+    Cold (left) or Warm (right)",
+    "Feeling towards Republican
+    Cold (left) or Warm (right)",
+    "Feeling towards Trump
+    Cold (left) or Warm (right)",
+    "Understand Democratic POV",
+    "Understand Republican POV"
+  ))))
+
+graph_data |>
+  ggplot(aes(x = name, y = mean, color = party)) +
+  geom_point(position = position_dodge(width = -0.2)) +
+  geom_errorbar(aes(ymin = mean - abs(1.96 * sd), ymax = mean + abs(1.96 * sd)),
+                position = position_dodge(width = -0.2),
+                width = 0.2) + 
+  geom_hline(yintercept = 0) +
+  theme_minimal() +
+  coord_flip(expand = TRUE) +
+  labs(x = "Political opinions",
+       y = "Difference from baseline (standard deviation)",
+       color = "Party") +
+  scale_color_manual(values = c("dodgerblue3", "springgreen3", "firebrick3"))
+```
+
 # Result
-Figure 1
-It shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
+
+Figure 1 It shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
 In this graph, the x-axis is the difference from the baseline, the y-axis is the subjective well-being, the orange line is the control group, the blue line is the treatment group, and the confidence interval is 95%.
@@
 
-Figure 2
-These two figures show the distribution of Facebook usage at Baseline and Endline.
+Figure 2 These two figures show the distribution of Facebook usage at Baseline and Endline.
 The red is the control group and the green is the treatment group.
@@
 
-Figure 3
-The above two figures show whether Facebook usage makes social life worse or better.
+Figure 3 The above two figures show whether Facebook usage makes social life worse or better.
 The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale.

### 2024-02-15 scripts/00-simulate_data.R

@@ -1,16 +1,18 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates the analysis data from 01-data_cleaning
+# Author: Kenneth Chan, Stephanie Xuan Zhao and Siyu Li
+# Date: 15 February 2023 
+# Contact: chif.chan@mail.utoronto.ca,
+#          xuan.zhao@mail.utoronto.ca,
+#          siyul.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Digital addiction by Hunt Allcott, Matthew Gentzkow and
+#                 Lena Song
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
 # [...ADD CODE HERE...]

### 2024-02-15 scripts/01-data_cleaning.R

@@ -2,12 +2,14 @@
 # Purpose: Cleans the raw data recorded by Hunt Allcot, Luca Braghieri, 
 #          Sarah Eichmeyer and Matthew Gentzkow
 # Author: Kenneth Chan, Stephanie Xuan Zhao and Siyu Li
-# Date: 11 February 2023 
-# Contact: kenchancf0618@gmail.com
+# Date: 15 February 2023 
+# Contact: chif.chan@mail.utoronto.ca,
+#          xuan.zhao@mail.utoronto.ca,
+#          siyul.li@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Digital addiction by Hunt Allcott, Matthew Gentzkow and
 #                 Lena Song
-# Any other information needed? None
+# Any other information needed? Data from original replication package
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-02-15 scripts/02-test_data.R

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Tests... 
-# Author: 
-# Date: 11 February 2023 
-# Contact: 
+# Purpose: Tests the data from 01-data_cleaning 
+# Author: Kenneth Chan, Stephanie Xuan Zhao and Siyu Li
+# Date: 15 February 2023 
+# Contact: chif.chan@mail.utoronto.ca,
+#          xuan.zhao@mail.utoronto.ca,
+#          siyul.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-# Any other information needed? 
+# Pre-requisites: Digital addiction by Hunt Allcott, Matthew Gentzkow and
+#                 Lena Song
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-02-15 scripts/99-replications.R

@@ -2,7 +2,9 @@
 # Purpose: Replicated graphs from Digital addiction
 # Author: Kenneth Chan, 
 # Date: 11 February 2023 
-# Contact: kenchancf0618@gmail.com
+# Contact: chif.chan@mail.utoronto.ca,
+#          xuan.zhao@mail.utoronto.ca,
+#          siyul.li@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Digital addiction by Hunt Allcott, Matthew Gentzkow and
 #                 Lena Song
@@ -294,7 +296,6 @@ ggarrange(
 ########################
 count_participant <- count(all_data)
 
-
 ### Distribution of republican, democrat and independent ###
 graph_data <- all_data |>
   group_by(repdem) |>
@@ -422,7 +423,8 @@ graph_data |>
   coord_flip(expand = TRUE) +
   labs(x = "Political opinions",
        y = "Difference from baseline (standard deviation)",
-       color = "Party")
+       color = "Party") +
+  scale_color_manual(values = c("dodgerblue3", "springgreen3", "firebrick3"))
 
 # Clean enviroment
 rm(list = ls())

### 2024-02-15 scripts/00-simulate_data.R
Add simulation code

@@ -15,7 +15,57 @@
 library(tidyverse)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
 
+simulated_facebook_minutes <- 
+  tibble(
+    id = (1:400),
+    fb_minutes = rpois(
+      n = 400,
+      lambda = 100
+    ),
+    type = c(
+      rep(x = "Control", times = 200),
+      rep(x = "Treatment", times = 200)
+    )
+)
+
+simulated_well_being <-
+  tibble(
+    id = rep(x = (1:400), times = 16),
+    name = rep(x = c(
+      "Facebook minutes",
+      "Happiness",
+      "Relative happiness to peers",
+      "Life is ideal",
+      "Conditions of life is excellent",
+      "Satisfied with life",
+      "Well being index",
+      "Lack companion",
+      "Feeling left out",
+      "Feel isolated",
+      "Social index",
+      "Bored(-1)",
+      "Anxious(-1)",
+      "Depressed(-1)",
+      "Absorbed in doing something worthwhile",
+      "Feeling index"
+      ),
+      times = 400),
+    type = c(
+      rep(x = "Control", times = 200*16),
+      rep(x = "Treatment", times = 200*16)
+    ),
+    temp_level =
+      rpois(
+        n = 400*16, lambda = 5
+      ), # Draw 6400 times from the poisson distribution
+    level = ifelse(temp_level > 5, 5, temp_level) # limit the maximum level
+  ) |>
+  select(-temp_level)
+
+max(simulated_well_being$level)
+
+# Clean environment
+rm(list = ls())
 
 

### 2024-02-15 paper/paper.qmd
add cross reference and label for figures

@@
 
+In our paper, we use a dataset for users who most focus on using Facebook as social media.
+The experiment has two periods which are baseline and endline.
+The research target is separate into control and treatment groups, for the control group, they can themselves and for the treatment group they can get treatment if they achieve goals about self-control for using social media.
+At the beginning of the experiment, the research targets finish a survey about how their mental health works at that time and other information like political trends and knowledge they get from the news.
+After four weeks, both groups of research targets wrote the survey and it shows there are differences between them.
+Both groups have a significant change for baseline and end line.
+The control group have a worse performance than the treatment group.
+
 # Data
 
-The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions :
+## Methodological Approach
+The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of six questions, based on the different responses it is possible to categorize and collect new data.
 
--   "...I was a happy person."
--   "...I was satisfied with my I felt anxious."
--   "...I felt depressed."
--   "...I could concentrate on my life."
--   "...I could concentrate on what I was doing."
--   "...I was easily distracted."
--   "... I slept well."
+## Survey Measures:
+The research includes several variables related to social media and examines the effects of different groups of experimenters in experiments with different time regimes for social media use.
+The nature and severity of digital addiction are relevant to many important issues, and the authors adopted economic models of digital addiction, using randomized experiments to provide unmodeled evidence and estimate model parameters that would simulate the effects of habit formation and self-control issues on smartphone use, and these valuations would also directly affect the experimenter's reference data.
 
-Based on the different responses it is possible to categorize and collect new data.
+# Result
 
 ```{r}
-#| label: fig-1
-#| fig-cap: figure 1 cap
+#| label: fig-usage_time
+#| fig-cap: Facebook Usage Time at Baseline And Endline
 #| echo: false
@@
 
+These figure(@fig-usage_time) show the distribution of Facebook usage at Baseline and Endline.
+The red is the control group and the green is the treatment group.
+The Y-axis shows the fraction of the sample and the x-axis shows Facebook usage time.
+For the longest time, the endline group’s time is shorter than the baseline’s time and the longest time both happen in the control group.
+The longest time for the treatment group is 550 minutes in baseline and 450 minutes in the endline group.
+For the treatment group, it decreases from 625 minutes to 575 minutes.
+To this result, there is a large decrease for the longest usage time.
+For the baseline, usage time exceeding 250 minutes is more than 2.5% in total but compared with it, at the endline, for the control group it has around 5% and for treatment is only 1.25%.
+
+It is obvious that between 0 and 125 minutes, the figure has a skew left and generally fraction decreases for each period in the treatment group.
+
 ```{r}
-#| label: fig-2
-#| fig-cap: figure 2 cap
+#| label: fig-swb
+#| fig-cap: Difference at Baseline for Subjective Well-Being
 #| echo: false
@@
 
+Above figure(@fig-swb) shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
+In this graph, the x-axis is the difference from the baseline, the y-axis is the subjective well-being, the orange line is the control group, the blue line is the treatment group, and the confidence interval is 95%.
+The treatment group was controlled by the researcher for the amount of time spent on Facebook per day and was rewarded accordingly for being controlled.
+The research target also generally responded that receiving the reward mechanism could greatly improve their subjective well-being.
+In contrast, there was not much change in the other survey directions.
+From the figure we can also see that the difference between the values of happiness, and conditions of life is excellent is not big, they are all concentrated in the range of -0.25 to 0.25.
+The subjective happiness of the treatment group will be a little bit lower than that of the control group at this time.
+
+The graph above shows the result of deactivation of the first 4 weeks, treatment means there is bonus cash if they successfully deactivate for another 4 weeks (8 weeks in total)
+
+* Unit is the standard deviation of the baseline
+* Well being an index is the sum of (Happiness, … and satisfaction with life)
+* The social index is the sum of (Lack companion, …, Feel isolated)
+* The feeling index is the sum of (Bored, …, Absorbed in doing)
+
 ```{r}
-#| label: fig-3
-#| fig-cap: figure 3 cap
+#| label: fig-social_life
+#| fig-cap: Facebook Make Social Life Worse or Better at Baseline And Endline Period
 #| echo: false 
@@
 
+Figure 3 
+The above figure(@fig-social_life) show whether Facebook usage makes social life worse or better.
+The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale.
+From the figure, it has changed between -1 and 1.
+At baseline, it has the most fraction at 0 for the treatment group and in the control group, it has the most in -1 and 0.
+However, in endline’s figure, the biggest fraction shifts to the right.
+It becomes 0 and 1.
+This means that user feels their social life becomes better.
+This helps to prove that with less time spent on Facebook, people’s objective well-being increases.
+
 ```{r}
-#| label: fig-4
-#| fig-cap: figure 4 cap
+#| label: fig-political_opinion_1
+#| fig-cap: People Political Opinion 1
 #| echo: false
@@
 ```{r}
-#| label: fig-5
-#| fig-cap: figure 5 cap
+#| label: fig-political_opinion_2
+#| fig-cap: People Political Opinion 2
 #| echo: false
@@
 ```
+
+This two graphs(@fig-political_opinion_1)(@fig-political_opinion_2) shows whether people change their political stance when using Facebook or not.
+The two different political positions are Republican, Democrat or Independent and Liberal or Conservative.
+obviously, we can see from the Republican graph that most people would still strongly choose Strongly Democratic, almost to 0.3 The distance is almost 0.3.
+In the Liberal graph, we can see that most people would choose liberal over extremely liberal, with a figure of more than 0.3.
 
@@
 
-# Result
-
-Figure 1 It shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
-In this graph, the x-axis is the difference from the baseline, the y-axis is the subjective well-being, the orange line is the control group, the blue line is the treatment group, and the confidence interval is 95%.
-The treatment group was controlled by the researcher for the amount of time spent on Facebook per day and was rewarded accordingly for being controlled.
-The research target also generally responded that receiving the reward mechanism could greatly improve their subjective well-being.
-In contrast, there was not much change in the other survey directions.
-From the figure we can also see that the difference between the values of happiness, and conditions of life is excellent is not big, they are all concentrated in the range of -0.25 to 0.25.
-The subjective happiness of the treatment group will be a little bit lower than that of the control group at this time.
-
-Figure 2 These two figures show the distribution of Facebook usage at Baseline and Endline.
-The red is the control group and the green is the treatment group.
-The Y-axis shows the fraction of the sample and the x-axis shows Facebook usage time.
-For the longest time, the endline group’s time is shorter than the baseline’s time and the longest time both happen in the control group.
-The longest time for the treatment group is 550 minutes in baseline and 450 minutes in the endline group.
-For the treatment group, it decreases from 625 minutes to 575 minutes.
-To this result, there is a large decrease for the longest usage time.
-For the baseline, usage time exceeding 250 minutes is more than 2.5% in total but compared with it, at the endline, for the control group it has around 5% and for treatment is only 1.25%.
-
-It is obvious that between 0 and 125 minutes, the figure has a skew left and generally fraction decreases for each period in the treatment group.
-
-Figure 3 The above two figures show whether Facebook usage makes social life worse or better.
-The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale.
-From the figure, it has changed between -1 and 1.
-At baseline, it has the most fraction at 0 for the treatment group and in the control group, it has the most in -1 and 0.
-However, in endline’s figure, the biggest fraction shifts to the right.
-It becomes 0 and 1.
-This means that user feels their social life becomes better.
-
-Figure 4
-
 # Discuss

### 2024-02-15 paper/paper.qmd
add cross reference and label for figures

@@
 title: "Digital Addiction"
-subtitle: "My subtitle if needed"
+subtitle: "Analysis of How Usage of Social Media Impact Objective Well-Being And Political Opinion"
 author: 

### 2024-02-15 paper/paper.qmd
Add table of content

--- 2024-02-15 paper/paper.qmd
@@
 format: pdf
+toc: true
 number-sections: true

### 2024-02-15 paper/paper.qmd
add tool reference

--- 2024-02-15 paper/paper.qmd
@@
 format: pdf
+toc: true
 number-sections: true
-#bibliography: references.bib
+bibliography: references.bib
 ---
@@
 The nature and severity of digital addiction are relevant to many important issues, and the authors adopted economic models of digital addiction, using randomized experiments to provide unmodeled evidence and estimate model parameters that would simulate the effects of habit formation and self-control issues on smartphone use, and these valuations would also directly affect the experimenter's reference data.
+
+## Tool
+Our paper use data from While writing the paper, we have utilized different tools and literature references to ensure that the findings across the board were correctly logical.
+Our graphs and data analysis plots were laid using R code[@citeR] as a base.
+library tidyverse[@thereferencecanbewhatever] directly helped us to start from the data so that we can process and visualize the data for application in no time.
+library haven[@haven] to help us quickly convert the data we need into R language format.
+It can be convenient for us to import data into R for analysis and processing.
+library readxl[@readxl] helps us read some Excel functions and processing.
+This makes it easier for us to analyze Excel data in R.
+library janitor[@janitor] helps us to check and clean up the dirty data, and format the data we need in R.
+library ggpubr[@ggpubr] facilitates us to draw graphs to meet the research direction more easily.
+These tools help us to understand more deeply the direction of the research and the relationship between them.
 
@@
 # Discuss
+In recent years, the popularity of smartphones has greatly increased the use of social media.
+Social media, as a communication tool, works in the context of people's interactions, and the psychological changes induced by interpersonal interactions become the mediating variable between its use and well-being.
+Excessive use of social media has a negative impact on health and well-being.
+Our present investigation suggests that limiting the time spent on social media use may be beneficial to health and well-being.
+Research has noted a correlation between reduced social media use and improved mental health, and this latest controlled experiment provides further evidence of a causal relationship between reduced social media use and improved physical health.
+For those who were directly asked to reduce their social media use time and do something else with that time, they did not experience health benefits, suggesting that if one wants to get a person healthier to exercise, one should not ask them how to use their time, which can be counterproductive.
+
+There are some weaknesses of our experiment, that make our experiment lack generality.
+People in different age groups have different lifestyles and not all age groups have the same free time to use Facebook.
+For example, for seniors, some of them not familiar with smartphones and they do not understand how to use Facebook.
+Therefore, when they join the experiment, the experiment does not work as significantly as researchers expect.
+Also, different age groups can not have a more specific discussion about the actual situation of how people use Facebook.
+For example, Facebook is popular with people aged around 18-25 and those people, have more free time than people who have work, especially during summer vacation.
+This causes the experiment can not have generality.
+
+In the future, researchers can have a longer experiment and track the research target after finishing the experiment to see did they kept the habit that they had at the endline or if they increased usage time.
+With this tracking, the researcher can check what difference between the control group and the treatment group, and then check if there are any direct relations to show which group has self-control.
+Therefore, researchers can know did their experiment impacted the research targets’ lifestyles.
+Another thing, research can do to improve the experiment is to set different age groups thus, researchers can focus on how different age groups work and explore why there are differences between groups.
 

### 2024-02-15 paper/paper.qmd
add abstract

@@
 date-format: long
-abstract: "."
+abstract: "The global population of social media users is predicted to reach 4.95 billion by 2023; this is a significant increase from the 2.05 billion users in 2015 (source: Backlinko).
+As technology continues to evolve, smartphones are playing an increasingly important role in our daily lives, providing us with more and more services.
+However, the impact of smartphones on our lives still needs to be further explored.
+In this paper, we will discuss two aspects.
+First, we explore the impact of the social media Facebook on social and political attitudes, providing insights and calling for further research on interventions to mitigate its negative effects.
+The paper analyzes experimental data related to subjective well-being by experimentally surveying participants and using an analytic factorial design to randomize them into reward and restriction groups.
+The study uses regression modelling to assess the impact of specific digital technology use patterns on well-being.
+We also examine whether Facebook use affects people's political attitudes."
 format: pdf
@@
 
-Figure 3 
 The above figure(@fig-social_life) show whether Facebook usage makes social life worse or better.
@@
 
-This two graphs(@fig-political_opinion_1)(@fig-political_opinion_2) shows whether people change their political stance when using Facebook or not.
+This graphs(@fig-political_opinion_1)(@fig-political_opinion_2) shows whether people change their political stance when using Facebook or not.
 The two different political positions are Republican, Democrat or Independent and Liberal or Conservative.
@@
 In the Liberal graph, we can see that most people would choose liberal over extremely liberal, with a figure of more than 0.3.
+So from this graph social media affects a lot of people who are liberal and conservatives are in the minority.
 

### 2024-02-15 paper/paper.qmd
add reference

@@
 In research pertaining to mobile phone usage, control and restriction groups can be employed to evaluate the effects of interventions on cell phone use as well as the effects of cell phone use on an individual's behaviour or psychological state.
+
+Our paper is followed by a reproduction of Hunt Allcott, Matthew Gentzkow, and Lena Song’s analysis[@originalpaper] of digital addiction to social media and their experiments prove reducing the usage of social media incentive new habits.
+Furthermore, their model shows that self-control is one of the important problems for people and it causes 31 percent of social media use.
 

### 2024-02-15 paper/paper.qmd
add variable

@@
 The experiment has two periods which are baseline and endline.
-The research target is separate into control and treatment groups, for the control group, they can themselves and for the treatment group they can get treatment if they achieve goals about self-control for using social media.
+The research target is separated into control and treatment groups, for the control group, they can themselves and the treatment group they can get treatment if they achieve goals about self-control for using social media.
 At the beginning of the experiment, the research targets finish a survey about how their mental health works at that time and other information like political trends and knowledge they get from the news.
@@
 The control group have a worse performance than the treatment group.
+
+In our research, we chose to compare the two groups about their change.
+At the endline, it shows that objective well-being is higher when people use less Facebook and using Facebook cause polarizing political opinions to happen for people to use Facebook.
 
@@
 These tools help us to understand more deeply the direction of the research and the relationship between them.
+
+## Variable
+In our experiment, the dataset includes three surveys and we only select two of them to analyze.
+The first survey is the baseline and the survey after 4 weeks of the experiment is endline.
+The first survey To analyze Facebook usage time, we collect usage time for each research target.
+For this part, it has only one variable which is how much time each one spends on Facebook at the baseline and endline.
+The second figure, measures objective well-being for each research target at baseline and endline.
+It asks the research target to choose what they feel like at that time and count it together.
+Each variable score has five choices which are
+
+* Strongly disagree
+* Disagree
+* Slightly disagree
+* Neither agree nor disagree
+* Slightly agree
+* Agree
+* Strongly agree
+
+ To count it, the different variables are stated below
+
+* My life is close to ideal: 
+* The condition of my life is excellent
+* Satisfied with my life
+* How often did you feel that you lacked companionship over the past four weeks?
+* How often do you feel left out over the past four weeks?
+* How often did you feel isolated from others over the past four weeks?
+
+Also, it has choice for how much time people spend with four different emotions which are
+
+* Felt bored
+* Felt anxious
+* Felt depressed
+* Absorbed in something worthwhile
+
+For each motion, it have four different levels which are
+
+* Level 1: None or almost none of the time
+* Level 2: Feel a little bit of time
+* Level 3: Sometimes feel it
+* Level 4: All or almost of the time
+
+With those variables, researchers can have a more general idea about how research targets mental health.
+
+To analyze the political opinion of the research target, the researcher also provides several choices for people.
+People choose what they feel about the political opinion they have.
+Those variables are:
+
+* Republican(Strongly Republican)
+* Republican(Weakly Republican)
+* Independent(Lean toward the Republican Party)
+* Independent
+* Independent(Lean toward the Democratic Party)
+* Democrat(Weakly Democratic)
+* Democrat(Strongly Democratic)
+
+Also, researchers ask about the level of extreme people have, therefore, people can choose the variables below:
+
+* Extreme conservative
+* Conservative
+* Slightly Conservative
+* Moderate
+* Slightly Liberal
+* Liberal
+* Extreme Liberal
+By collecting those data, we can know how extreme political opinions people have.
 
@@
 ```
-
-Above figure(@fig-swb) shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
+Figure(@fig-swb) shows dot plots that count the differences between two different groups in all directions of the survey, and explains the results of the control and treatment groups in the Subjective Well-Being of the survey.
 In this graph, the x-axis is the difference from the baseline, the y-axis is the subjective well-being, the orange line is the control group, the blue line is the treatment group, and the confidence interval is 95%.
@@
 
-The above figure(@fig-social_life) show whether Facebook usage makes social life worse or better.
+The below figure(@fig-social_life) show whether Facebook usage makes social life worse or better.
 The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale.
@@
 
-# Discuss
+# Discussion
 In recent years, the popularity of smartphones has greatly increased the use of social media.
